Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/intro.tex
added outline of dissertation to chap 1

ADD ONCE COMPLETE

>>>>

This dissertation is organized as follows. Chapter \ref{chap:pogm} introduces a novel approach to solve for the exact Bayesian probability of grid cells in real-time. Then, Chapter \ref{chap:ae2D} extends these contributions to autonomous exploration in 2D space, where a novel approach to predict future map uncertainty is presented. Next, Chapter \ref{chap:ae2D} applies the proposed occupancy grid mapping approach to 3D environments, and presents a method to simplify autonomous exploration in 3D environments with map projections. Chapter \ref{chap:multivehicle} applies this 3D mapping and exploration to multi-vehicle exploration and patrol scenarios using a bidding-based framework. Then, Chapter \ref{chap:ae3Dcomplex} extends exploration to complex 3D environments without 2D map projections. In these chapters, several numerical examples demonstrate the efficacies of the approaches. Furthermore, Chapter \ref{chap:Experiments} presents three experiments, which show the key contributions in this dissertation. Finally, these are followed by conclusions in Chapter \ref{chap:Conclusions}.
